---
output:
  pdf_document:
    toc: false
    includes:
       in_header: preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---


\centerline{\includegraphics[width=4cm]{codecheck_logo.pdf}}

\vspace*{2cm}


```{r rsetup-knitr,eval=TRUE,include=FALSE}
require(knitr)
require(xtable)
require(yaml)
require(tibble)
require(readr)
require(rprojroot)
options(width=60)
opts_chunk$set(cache=FALSE)

yml_file = "codecheck.yml"
root_project = find_root(yml_file)
dest_dir = file.path(root_project, "codecheck", "outputs")

yaml_data = read_yaml( file.path(root_project, yml_file) )

manifest = yaml_data$manifest

## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

copy_files_to_dest_dir = function(root_project,
                                  manifest,
                                  dest_dir,
                                  keep_full_path=FALSE) {
  ## Copy each file mentioned in MANIFEST into DEST_DIR.
  ## If KEEP_FULL_PATH is TRUE, we keep the full path for the output files.
  ## This is useful when there are two output files with the same name in
  ## different folders, e.g. expt1/out.pdf and expt2/out.pdf
  ##
  ## Return a vector of the names of the files created.
  outputs = sapply(manifest, function(x) x$file)
  src_files = file.path(root_project, outputs)
  missing = !file.exists(src_files)
  if (any(missing)) {
    err = paste("Manifest files missing:\n",
                paste(src_files[missing], sep='\n'))
    stop(err)
  }

  dest_files = file.path(dest_dir,
                         if ( keep_full_path) outputs else basename(outputs))
  file.copy(src_files, dest_files, overwrite=TRUE)
  dest_files
}

  
get_outputs = function(manifest) {
  files = sapply(manifest, function(x) x$file)
  comments = sapply(manifest, function(x) x$comment)
  sizes = file.size(dest_files)
  url=sprintf('<a href="%s">%s</a>', dest_files, files)
  table = cbind(files, comments, sizes, url)
  table
}

dest_files = copy_files_to_dest_dir(root_project, manifest,
                                    dest_dir, keep_full_path=FALSE)
                                    
```


```{r,include=FALSE}
## Temporary hack to make URL
url_it = function(url) {
  url = sub("<", "\\\\url{", url)
  url = sub(">", "}", url)
  url
}
```

---
title: `r paste("CODECHECK certificate", yaml_data$certificate)`
subtitle: `r url_it(yaml_data$report)`
---


```{r, include=FALSE}
codecheckers <- function(y) {
  checker = y$codechecker[[1]]
  paste(checker$name, url_it(checker$ORCID))
}

authors <- function(y) {
  authors = y$paper$authors
  num_authors = length(authors)
  for (i in 1:num_authors)
    if (i==1) {
      author_list = authors[[i]]
    } else {
      author_list = paste(author_list, authors[[i]], sep=', ')
    }
  author_list
}

```

```{r,include=FALSE}
summary_entries = list(
  "Title" =            yaml_data$paper$title,
  "Authors" =          authors(yaml_data),
  "Reference" =        url_it(yaml_data$paper$reference),
  "Codechecker" =      codecheckers(yaml_data),
  "Date of check:" =   yaml_data$check_time,
  "Summary:" =         yaml_data$summary,
  "Repository:" =      url_it(yaml_data$repository))
summary_df = data.frame(Item=names(summary_entries),
                Value=unlist(summary_entries, use.names=FALSE))
```


```{r,echo=FALSE,results='asis'}
##kable(df, booktabs=FALSE, align=c('l', 'p{12cm}'), caption="CODECHECK Summary")
print(xtable(summary_df, align=c('l', 'l', 'p{10cm}'),
             caption='CODECHECK summary'),
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```


```{r, echo=FALSE,results='asis'}
outputs = get_outputs(manifest)
xt = xtable(outputs[,1:3], caption="Summary of output files generated")
colnames(xt) = c("File", "Comment", "Size")
print(xt,
      include.rownames=FALSE,
      comment=FALSE)
```


# Summary

I was able to reproduce the figures and tables in the paper.  The
simulations took several days to run, and so in the codechecker repo I
have included the results of the simulations (the `*.qs` files).  The
figures however are not included in the main section of the repo, but
are in the `codecheck/outputs` folder.


\clearpage

# CODECHECKER notes

The github repo <https://github.com/cmmid/covid-uk> contained all the
necessary code.  I needed some
system installations and R packages, but then was able to run the code.


## Extra software installations

Several extra linux and R packages were required.  These are
documented in the file `install.R`, shown here:

```{r, code = readLines("../install.R"), eval=FALSE}
```

I ran this on arch linux, but a Dockerfile is also available.



## Running the software to regenerate outputs.

The only significant change to the two scripts was to ensure covid
path was the current directory WITH a trailing slash.

```{r eval=FALSE}
covid_uk_path = "./"
```


I created a script to run the jobs in parallel on a cluster, `run-jobs.sh`.

```{bash, code = readLines("../run-jobs.sh"), eval=FALSE}
```

The `*.stdout` files capture the output from each run; for each run,
there are two output files, e.g. for run 1: `1-dynamics.qs` and
`1-totals.qs`.  These `*.qs` files are then processed by the script
`UK-view.R` to make the output figures.

```{bash, eval=FALSE}
Rscript UK-view.R
```

\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}


\clearpage
```{r echo=FALSE, fig.cap=outputs[1, "comments"]}
knitr::include_graphics(dest_files[1])
```

\clearpage


<!-- The tables are quite wide, so we reduce the font size so that we -->
<!-- can fit onto the page; could also use sidewaystable but that is a -->
<!-- bit clunky. -->
```{r, echo=FALSE, results='asis'}
tab12week = read.csv(dest_files[2])
print(xtable(tab12week, 
             caption=outputs[2, "comments"]),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```

\clearpage
```{r echo=FALSE, fig.cap=outputs[3, "comments"]}
knitr::include_graphics(dest_files[3])
```

\clearpage
```{r echo=FALSE, fig.cap=outputs[4, "comments"]}
knitr::include_graphics(dest_files[4])
```

\clearpage
```{r echo=FALSE, fig.cap=outputs[5, "comments"]}
knitr::include_graphics(dest_files[5])
```


\clearpage

```{r, echo=FALSE, results='asis'}
lockdown = read.csv(dest_files[6])
print(xtable(lockdown, 
             caption=outputs[6, "comments"]),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      ##floating = TRUE, floating.environment = "sidewaystable",
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```

\clearpage

```{r, echo=FALSE, results='asis'}
print(xtable(read.csv(dest_files[7]),
             caption=outputs[7, "comments"]),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      floating = TRUE, floating.environment = "sidewaystable",
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```

\clearpage
```{r, echo=FALSE, results='asis'}
print(xtable(read.csv(dest_files[8]),
             caption=outputs[8, "comments"]),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      ##floating = TRUE, floating.environment = "sidewaystable",
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```

\clearpage
```{r, echo=FALSE, results='asis'}
print(xtable(read.csv(dest_files[9]),
             caption=outputs[9, "comments"]),
      size="\\fontsize{6pt}{7pt}\\selectfont",
      ##floating = TRUE, floating.environment = "sidewaystable",
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```




\clearpage
# About this document

This document was created using Rmarkdown.  `make codecheck.pdf` will
regenerate the file.

```{r}
sessionInfo()
```




<!-- 
  rmarkdown::render("davies2020-codecheck.Rmd", output_format="pdf_document") 
  -->
